PANCHANGE_data_preprocessing

### 2020-08-20 PANCHANGE_data_preprocessing2020-07-15.Rmd
corrected PCL retro coding

```{r coping ramp pcl cleaning}
if(RAMP == TRUE) {
coping.ramp.pcl.raw.id <- coping.ramp.pcl.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_reminded_upset, # differ to RAMP prepan
    pcl.stressful_situation_avoiding_activities_base = pcl.stressful_experience_avoiding_activities, # differ to RAMP prepan
    pcl.cut_people_feeling_distant_base = pcl.feeling_distant_cut_people, # differ
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_reminded_upset.1, # differ
    pcl.stressful_situation_avoiding_activities_retro = pcl.stressful_experience_avoiding_activities.1, # differ
    pcl.cut_people_feeling_distant_retro = pcl.feeling_distant_cut_people.1, # differ
    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

@@

# Look at values
coping.pcl.raw.id %>%
  descr(pcl.sum_score_base_raw,
        stats = "common"
  )
```

>>>>

```{r coping ramp pcl cleaning}
if(RAMP == TRUE) {
coping.ramp.pcl.raw.id <- coping.ramp.pcl.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_reminded_upset, # differ to RAMP prepan
    pcl.stressful_situation_avoiding_activities_base = pcl.stressful_experience_avoiding_activities, # differ to RAMP prepan
    pcl.cut_people_feeling_distant_base = pcl.feeling_distant_cut_people, # differ
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro_unc = pcl.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro_unc = pcl.stressful_experience_reminded_upset.1, # differ
    pcl.stressful_situation_avoiding_activities_retro_unc = pcl.stressful_experience_avoiding_activities.1, # differ
    pcl.cut_people_feeling_distant_retro_unc = pcl.feeling_distant_cut_people.1, # differ
    pcl.feeling_irritable_or_having_angry_outbursts_retro_unc = pcl.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro_unc = pcl.difficulty_concentrating.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

Recode RAMP PCL retro scores
```{r recode ramp pcl retro scores}
if(RAMP == TRUE) {

pcl_retro_numeric_recode_vars <- c(
    "pcl.stressful_experience_repeated_images_retro_unc_numeric",
    "pcl.stressful_experience_upset_reminded_retro_unc_numeric",
    "pcl.stressful_situation_avoiding_activities_retro_unc_numeric",
    "pcl.cut_people_feeling_distant_retro_unc_numeric",
    "pcl.feeling_irritable_or_having_angry_outbursts_retro_unc_numeric",
    "pcl.difficulty_concentrating_retro_unc_numeric"
)

#recode and rename numeric retro items
coping.pcl.raw.id <- coping.pcl.raw.id %>%
  mutate_at(vars(all_of(pcl_retro_numeric_recode_vars)),
    ~ recode(.,
           `1` = 1, # 1 = Yes = 1
           `2` = 0, # 2 = No = 0
           `3` = NA_real_ # NA = 3 = NA
                   )) %>%
  rename_at(vars(ends_with("_retro_unc_numeric")), 
            funs(str_replace(., 
                             "_retro_unc_numeric", 
                             "_retro_numeric")
                 )
            )

pcl_retro_recode_vars <- c(
    "pcl.stressful_experience_repeated_images_retro_numeric",
    "pcl.stressful_experience_upset_reminded_retro_numeric",
    "pcl.stressful_situation_avoiding_activities_retro_numeric",
    "pcl.cut_people_feeling_distant_retro_numeric",
    "pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric",
    "pcl.difficulty_concentrating_retro_numeric"
)

#create factor versions 
coping.pcl.raw.id <- coping.pcl.raw.id %>%
  mutate_at(vars(
    all_of(pcl_retro_recode_vars)),
    list("factor" = 
            ~ recode_factor(.,
           "1" = "Yes", # 1 = Yes = 1
           "0" = "No" # 2 = No = 0
                   ))) %>%
  rename_at(vars(ends_with( "retro_numeric_factor")), 
            list(~gsub(
              pattern = "_retro_numeric_factor",
              replacement = "_retro",
              .)
              )
            ) %>%
  select(
    -ends_with("unc")
  )
}

colnames(coping.pcl.raw.id)
```

@@

# Look at values
coping.pcl.raw.id %>%
  descr(pcl.sum_score_base_raw,
        stats = "common"
  )
